---
title: "Showroom Performance"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=F, asis=T)
library(dplyr)
library(stringr)
library(openxlsx)
library(ggplot2)
library(tidyr)
library(scales)
library(knitr)
library(lubridate)
library(gridExtra)
Payment <- read.csv("../Clover/Sales240813-241230/Payments-20240909-20241231.csv", as.is = T) %>% mutate(Date = as.Date(gsub(" .*", "", Payment.Date), format = "%d-%b-%Y"), Month = format(Date, "%b"), DayOfWeek = format(Date, "%a")) %>% filter(Result == "SUCCESS", Amount != 0) %>% select(Date, Month, DayOfWeek, Tender, Amount, Tax.Amount, Customer.Name, Payment.ID)
Refund <- read.csv("../Clover/Sales240813-241230/Refunds-20240909-20241231.csv", as.is = T) %>% mutate(Date = as.Date(gsub(" .*", "", Refund.Date), format = "%d-%b-%Y"), Month = format(Date, "%b"), DayOfWeek = format(Date, "%a")) %>% select(Date, Month, DayOfWeek, Refund.Amount, Refund.ID)
Payment_daily <- Payment %>% group_by(Date) %>% summarise(Amount = sum(Amount), N = n())
days <- seq(from = as.Date("2024-09-09"), to = as.Date("2024-12-24"), by = "days")
workdays <- days[wday(days) != 1 & !days %in% c("2024-10-14", "2024-11-11")]
Payment_daily <- rbind(Payment_daily, data.frame(Date = workdays[!workdays %in% Payment_daily$Date], Amount = 0, N = 0)) %>% arrange(Date)
JJR_payment <- read.csv("../Clover/Sales240813-241230/JJR-orders-20240909-20241224.csv", as.is = T) %>% distinct(Order.Number, .keep_all = T) %>% mutate(Date = as.Date(gsub(" .*", "", Order.Date))) %>% filter(Shipping.Zone == "Canada BC", Date < "2024-12-25")
```

This is report of Richmond showroom performance from Sept 09 2024 (NetSuite integration) to Dec 24 2024.  

## Summary

  * Total Revenue:  __`r dollar(sum(Payment$Amount), accuracy = 0.01)`__ (Website BC at the same time period __`r dollar(sum(JJR_payment$Order.Total.Amount), accuracy = 0.01)`__, __`r percent(sum(Payment$Amount)/sum(JJR_payment$Order.Total.Amount))`__)
  * Total No. of orders:  __`r nrow(Payment)`__ (Website BC at the same time period __`r nrow(JJR_payment)`__, __`r percent(nrow(Payment)/nrow(JJR_payment))`__)
  * Total Refund:  __`r dollar(sum(Refund$Refund.Amount), accuracy = 0.01)`__ 
  * Total No. of refunds:  __`r nrow(Refund)`__ (__`r percent(nrow(Refund)/nrow(Payment))`__)
  * Average daily sales:  __`r dollar(mean(Payment_daily$Amount), accuracy = 0.01)`__
  * Average daily No. of orders:  __`r round(mean(Payment_daily$N))`__
  * Average order size:  __`r dollar(sum(Payment$Amount)/nrow(Payment), accuracy = 0.01)`__ 

```{r summary, fig.height=4, fig.width=12}
(trend <- ggplot(Payment, aes(Date, Amount)) + 
   geom_bar(stat = "identity", position = "stack", width = 0.8) + 
   ggtitle("Sales trend 2024-09-09 to 2024-12-31") + 
   theme_bw())
```

### Influence to JJ Website

  * JJ Website in Canada BC sales indeed show a significant decrease in Sept-Nov in 2024 compared to 2023 corresponding to Richmond showroom opening time.  
  * However, Website sales in Ontario and US as a whole also show some decrease in Sept and Oct in 2024, not as much as BC, so there may be other factors for the decrease other than offline purchases. 

```{r JJ, warning=F, fig.width=14}
JJR_2024 <- read.csv("../Clover/Sales240813-241230/JJR-orders-20240909-20241224.csv", as.is = T) %>%  distinct(Order.Number, .keep_all = T) %>% mutate(Date = as.Date(gsub(" .*", "", Order.Date)), Month = format(Date, "%b"), DayOfWeek = format(Date, "%a"), Year = "2024", Country = Country.Code..Shipping., State = ifelse(Country == "US", "US", State.Code..Shipping.)) %>% filter(Date < "2024-12-25") %>% group_by(Year, Month, Country, State) %>% summarise(No.of.Orders = n(), Amount = sum(Order.Total.Amount....Refund.)) %>% filter(Country != "", State != "")
JJR_2023 <- read.csv("../Clover/Sales240813-241230/JJR-orders-20230909-20231224.csv", as.is = T) %>%  distinct(Order.Number, .keep_all = T) %>% mutate(Date = as.Date(gsub(" .*", "", Order.Date)), Month = format(Date, "%b"), DayOfWeek = format(Date, "%a"), Year = "2023", Country = Country.Code..Shipping., State = ifelse(Country == "US", "US", State.Code..Shipping.)) %>% filter(Date < "2023-12-25") %>% group_by(Year, Month, Country, State) %>% summarise(No.of.Orders = n(), Amount = sum(Order.Total.Amount....Refund.)) %>% filter(Country != "", State != "")
JJR_23_24 <- rbind(JJR_2023, JJR_2024) %>% data.table::melt(id.vars = c("Year", "Month", "Country", "State"))
(JJR_23_24_CA <- ggplot(JJR_23_24, aes(factor(Month, levels = c("Sep", "Oct", "Nov", "Dec")), value, fill = Year)) + 
    geom_bar(position = position_dodge(), stat = "identity") + 
    facet_grid(variable ~ State, scales = "free") + 
    xlab("") + ylab("") + ggtitle("Website sales changes in Sept-Dec 2024") + 
    theme_bw())
```

### Sales by month
```{r month, fig.height=4, fig.width=12}
Payment_month <- Payment %>% group_by(Month) %>% summarise(Amount = sum(Amount), N = n()) %>% mutate(Average = Amount/N, Month = factor(Month, level = c("Sep", "Oct", "Nov", "Dec")))
Revenue_month <- ggplot(Payment_month, aes(Month, Amount)) + 
   geom_bar(stat = "identity", position = "stack", width = 0.8) + 
   ggtitle("Revenue by Month") + 
   theme_bw()
N_month <- ggplot(Payment_month, aes(Month, N)) + 
   geom_bar(stat = "identity", position = "stack", width = 0.8) + 
   ggtitle("No. of orders by Month") + 
   theme_bw()
Average_month <- ggplot(Payment_month, aes(Month, Average)) + 
   geom_bar(stat = "identity", position = "stack", width = 0.8) + 
   ggtitle("Average order size by Month") + 
   theme_bw()
grid.arrange(Revenue_month, N_month, Average_month, nrow = 1)
```

### Sales by day of week
```{r week, fig.height=4, fig.width=12}
Payment_week <- Payment %>% group_by(DayOfWeek) %>% summarise(Amount = sum(Amount), N = n()) %>% mutate(Average = Amount/N, DayOfWeek = factor(DayOfWeek, levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat")))
Revenue_week <- ggplot(Payment_week, aes(DayOfWeek, Amount)) + 
   geom_bar(stat = "identity", position = "stack", width = 0.8) + 
   ggtitle("Revenue by day of week") + 
   theme_bw()
N_week <- ggplot(Payment_week, aes(DayOfWeek, N)) + 
   geom_bar(stat = "identity", position = "stack", width = 0.8) + 
   ggtitle("No. of orders by day of week") + 
   theme_bw()
Average_week <- ggplot(Payment_week, aes(DayOfWeek, Average)) + 
   geom_bar(stat = "identity", position = "stack", width = 0.8) + 
   ggtitle("Average order size by day of week") + 
   theme_bw()
grid.arrange(Revenue_week, N_week, Average_week, nrow = 1)
```

### Sales by category

  * The top 5 best selling categories by quantity overall are: WJA, BTL, BTB, WPF, SWS
  * Top categories in each month are different

```{r category}
Category <- read.csv("../Clover/Sales240813-241230/LineItemsExport-20240909-20241231.csv", as.is = T)%>% mutate(Month = format(as.Date(gsub(" .*", "", Line.Item.Date), format = "%d-%b-%Y"), "%b"), Category = gsub("-.*", "", Item.Name)) %>% filter(Order.Payment.State == "Paid") %>% group_by(Category, Month) %>% summarise(Qty = n()) %>% arrange(Month, desc(Qty))
(Category_alltime <- ggplot(Category, aes(reorder(Category, Qty), Qty)) + 
    geom_bar(position = "stack", stat = "identity", width = 0.8) + 
    coord_flip(xlim = c(length(unique(Category$Category))-9, length(unique(Category$Category)))) + 
    xlab("") + ylab("") + 
    ggtitle("Top 10 best selling categories 2024-09-09 to 2024-12-24") +
    theme_bw())
Category_Sep <- ggplot(Category %>% filter(Month == "Sep"), aes(reorder(Category, Qty), Qty)) + 
    geom_bar(position = "identity", stat = "identity", width = 0.8) + 
    coord_flip(xlim = c(length(unique((Category %>% filter(Month == "Sep"))$Category))-9, length(unique((Category %>% filter(Month == "Sep"))$Category)))) + 
    xlab("") + ylab("") + 
    ggtitle("Top 10 in Sep") +
    theme_bw()
Category_Oct <- ggplot(Category %>% filter(Month == "Oct"), aes(reorder(Category, Qty), Qty)) + 
    geom_bar(position = "identity", stat = "identity", width = 0.8) + 
    coord_flip(xlim = c(length(unique((Category %>% filter(Month == "Oct"))$Category))-9, length(unique((Category %>% filter(Month == "Oct"))$Category)))) + 
    xlab("") + ylab("") + 
    ggtitle("Top 10 in Oct") +
    theme_bw()
Category_Nov <- ggplot(Category %>% filter(Month == "Nov"), aes(reorder(Category, Qty), Qty)) + 
    geom_bar(position = "identity", stat = "identity", width = 0.8) + 
    coord_flip(xlim = c(length(unique((Category %>% filter(Month == "Nov"))$Category))-9, length(unique((Category %>% filter(Month == "Nov"))$Category)))) + 
    xlab("") + ylab("") + 
    ggtitle("Top 10 in Nov") +
    theme_bw()
Category_Dec <- ggplot(Category %>% filter(Month == "Dec"), aes(reorder(Category, Qty), Qty)) + 
    geom_bar(position = "identity", stat = "identity", width = 0.8) + 
    coord_flip(xlim = c(length(unique((Category %>% filter(Month == "Dec"))$Category))-9, length(unique((Category %>% filter(Month == "Dec"))$Category)))) + 
    xlab("") + ylab("") + 
    ggtitle("Top 10 in Dec") +
    theme_bw()
grid.arrange(Category_Sep, Category_Oct, Category_Nov, Category_Dec, nrow = 2)
```

### Customer analysis

```{r customer}
customer <- read.csv(rownames(file.info(list.files(path = "../Clover/", pattern = "Customers-", full.names = TRUE)) %>% filter(mtime == max(mtime))), as.is = T) %>%
  mutate(Name = paste0(First.Name, " ", Last.Name)) %>% distinct(Email.Address, .keep_all = T) %>% filter(Name != " ", Email.Address != "") %>% `row.names<-`(.[, "Name"])
Customer_Clover <- Payment %>% mutate(Email = gsub("\\,.*", "", gsub('\\"', "", customer[Customer.Name, "Email.Address"]))) %>% group_by(Email) %>% summarise(N = n()) %>% filter(!is.na(Email))
new_Clover <- read.csv("../Clover/Sales240813-241230/non_included.csv", as.is = T) %>% filter(Email %in% Customer_Clover$Email)
new_website <- new_Clover %>% filter(Email %in% JJR_payment$Customer.User.Email)
Clover_website <- Customer_Clover %>% filter(Email %in% JJR_payment$Customer.User.Email)
```

  * No. of recorded customers: __`r nrow(Customer_Clover)`__
  * No. of repeat customers: __`r nrow(Customer_Clover %>% filter(N > 1))`__ (__`r percent(nrow(Customer_Clover %>% filter(N > 1))/nrow(Customer_Clover))`__)
  * Estimated No. of new customers from the showroom (not previously shopped on JJ website, but did not exclude those previously shopped on Amazon): __`r nrow(new_Clover)`__ (__`r percent(nrow(new_Clover)/nrow(Customer_Clover))`__) 
  * No. of new customers from the showroom who later on shopped on JJ website: __`r nrow(new_website)`__ (__`r percent(nrow(new_website)/nrow(new_Clover))`__)
  * No. of customers who shopped on both JJ website and showroom: __`r nrow(Clover_website)`__ (__`r percent(nrow(Clover_website)/nrow(Customer_Clover))`__ of all showroom customers)
  
### Inventory verification

  * Return quantities from refunds/exchanges are not included in the form below because it's very difficult to extract that information from Clover, hence the generally positive discrepancy (inventory at end of year more than transfers in - sales). KBS and SKB missing inventory are most likely due to some with missing barcode were sold under MISC. BRC discrepancy needs further investigating. 
  * We need to record refund/exchange separately. Please record all returns and exchanges in `TWK 2020 share\twk general\2 - show room operations\0-Return Exchange Tracking.xlsx` in the future. 


```{r discrepancy}
netsuite_item <- read.csv(rownames(file.info(list.files(path = "../NetSuite/", pattern = "Items_All_", full.names = TRUE)) %>% filter(mtime == max(mtime))), as.is = T)
start_inventory <- openxlsx::read.xlsx("../Clover/Archive/inventory20240909.xlsx", sheet = "Items") %>% filter(Name %in% netsuite_item$Name) %>% mutate(Quantity = ifelse(Quantity < 0, 0, Quantity)) %>% `row.names<-`(.[, "Name"])
end_inventory <- openxlsx::read.xlsx("../Clover/inventory20250102.xlsx", sheet = "Items") %>% filter(Name %in% netsuite_item$Name) %>% mutate(Quantity = ifelse(Quantity < 0, 0, Quantity)) %>% `row.names<-`(.[, "Name"])
SO <- read.csv("../Clover/Sales240813-241230/LineItemsGroupedByItem-20240909-20241231.csv", as.is = T) %>% group_by(Item.Name) %>% summarise(Qty = sum(X..of.Items.Sold)) %>% as.data.frame() %>% `row.names<-`(.[, "Item.Name"]) 
TO_out <- read.csv("../Clover/Sales240813-241230/TO_Surrey.csv", as.is = T) %>% `row.names<-`(.[, "ITEM"])
TO_in <- data.frame()
for(f in list.files("../Clover/Sales240813-241230/", pattern = "^order", full.names = T)){
  TO_in <- rbind(TO_in, read.csv(f, as.is = T))
}
TO_in <- TO_in %>% group_by(ITEM) %>% summarise(Qty = sum(Quantity)) %>% as.data.frame() %>% `row.names<-`(.[, "ITEM"]) 
discrepancy <- end_inventory %>% select(Name, Quantity) %>% mutate(start = start_inventory[Name, "Quantity"], TO_in = TO_in[Name, "Qty"], TO_out = TO_out[Name, "Quantity"], SO = SO[Name, "Qty"])
discrepancy[is.na(discrepancy)] <- 0
discrepancy <- discrepancy %>% mutate(discrepancy = Quantity - (start + TO_in -TO_out - SO)) %>% arrange(desc(abs(discrepancy))) %>% filter(discrepancy < -3 | discrepancy > 5)
kable(discrepancy, format = "simple", row.names = F, align = "lrrrrrr", caption = "List of items with discrepancy < -3 or > 5")
```
